Fast Neural Machine Translation Implementation

### 2018-05-17 wnmt.2018/wnmt.tex
turn on timings

This paper describe the submissions to the efficiency track for GPUs by members of the University of Edinburgh, Adam Mickiewicz University, Tilde and University of Alicante. We focus on efficient implementation of the recurrent deep-learning model as implemented in Amun, the fast inference engine for neural machine translation. We improve the performance with an efficient mini-batching and maxi-batching algorithm. Translation speed was also reduced by fusing the softmax operation with the beam seach algorithm.

@@

\begin{algorithm}[ht]
\begin{algorithmic}
\Procedure{Fused-Kernel}{vector $p$, bias vector $b$}

@@

\begin{figure}[ht]
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{fused.png}} 
\end{tabular}
\caption{Using fused operation}
\label{fig:fused}
\end{figure}

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 5.39 		& 5.38 (+0\%) \\ \hline
Add bias 	& 1.26		&  \\ 
Softmax 	& 1.69		& 2.07 (-86.6\%)\\
Beam search	& 12.53		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 3}}	\\ \hline	
Multiplication 	& 14.18 	& 14.16 (+0\%) \\ \hline
Add bias 	& 3.76		&  \\ 
Softmax 	& 4.75		& 3.43 (-87.1\%)\\
Beam search	& 18.23		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 9}}	\\ \hline	
Multiplication 	& 38.35 	& 38.42 (+0\%) \\ \hline
Add bias 	& 11.64		&  \\ 
Softmax 	& 14.4		& 17.5 (-72.1\%)\\
Beam search	& 36.7		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken (sec) breakdown}
\label{tab:fused-breakdown}
\end{table}

@@

\begin{table}[ht]
\begin{center}
\begin{tabular}{|l|r|r|} \hline
Beam size	& Baseline	& Tensor Cores \\ \hline
1	 	& 39.97 	& 34.54 (-13.6\%) \\ 
9 		& 145.8		& 116.8 (-20.0\%) \\ \hline
\end{tabular}
\end{center}
\caption{Time taken (sec) using Tensor Cores}
\label{tab:tensor-cores}
\end{table}

>>>>

This paper describe the submissions to the efficiency track for GPUs by members of the University of Edinburgh, Adam Mickiewicz University, Tilde and University of Alicante. We focus on efficient implementation of the recurrent deep-learning model as implemented in Amun, the fast inference engine for neural machine translation. We improve the performance with an efficient mini-batching algorithm and by fusing the softmax operation with the beam seach algorithm.

@@

\begin{algorithm}
\begin{algorithmic}
\Procedure{Fused-Kernel}{vector $p$, bias vector $b$}

@@

\begin{figure}
\centering
\begin{tabular}{cc}
{\includegraphics[scale=0.3]{fused.png}} 
\end{tabular}
\caption{Using fused operation}
\label{fig:fused}
\end{figure}

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|} \hline
		& Baseline	& Fused \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 1}}	\\ \hline	
Multiplication 	& 5.39 		& 5.38 (+0\%) \\ \hline
Add bias 	& 1.26		&  \\ 
Softmax 	& 1.69		& 2.07 (-86.6\%)\\
Beam search	& 12.53		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 3}}	\\ \hline	
Multiplication 	& 14.18 	& 14.16 (+0\%) \\ \hline
Add bias 	& 3.76		&  \\ 
Softmax 	& 4.75		& 3.43 (-87.1\%)\\
Beam search	& 18.23		&  \\ \hline
\multicolumn{3}{|c|}{\emph{Beam size 9}}	\\ \hline	
Multiplication 	& 38.35 	& 38.42 (+0\%) \\ \hline
Add bias 	& 11.64		&  \\ 
Softmax 	& 14.4		& 17.5 (-72.1\%)\\
Beam search	& 36.7		&  \\ \hline
\end{tabular}
\end{center}
\caption{Time taken (sec) breakdown}
\label{tab:fused-breakdown}
\end{table}

@@

\begin{table}
\begin{center}
\begin{tabular}{|l|r|r|} \hline
Beam size	& Baseline	& Tensor Cores \\ \hline
1	 	& 39.97 	& 34.54 (-13.6\%) \\ 
9 		& 145.8		& 116.8 (-20.0\%) \\ \hline
\end{tabular}
\end{center}
\caption{Time taken (sec) using Tensor Cores}
\label{tab:tensor-cores}
\end{table}
